---
title: "Assignment1.3.rmd"
author: "Lhavanya"
date: "5/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Data viz and wrangling

```{r}
library(tidyverse)
library(skimr)
```
```{r}
fastfood <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
```

2. Using `skimr` package provide a list of variables which types needs to be changed 
Use R function to identify the types of variables. What changes do you need to do to correctly record the types of variables? 
Does all variables have sufficient range (=variability) to be included? Which variable can be removed?

#Working with different data types

```{r}
skim(fastfood)
```

3. Identify variable(s) which should be factors and transform their type into a factor variable

# We need to convert our variables
```{r}

fastfood$restaurant<-as_factor(fastfood$restaurant)
fastfood$item<-as_factor(fastfood$item)
fastfood$salad<-as_factor(fastfood$salad)
skim(fastfood)
```


4. Replace NA in the dataset with 0 across all variables

```{r}
fastfood <- fastfood %>% replace(is.na(.), 0)
```


5. Create two new variables:
Read about `cut_number()` function using Help and add a new variable to the dataset `calories_type`. Use the function arguments to add labels `c("low", "med", "high")` and make the dataset ordered. Do not forget to save the updated dataset. 

#Create two new variables:


```{r}
fastfood <- fastfood %>%
  mutate(calories_type=cut_number(calories,3,labels=c("low", "med", "high"),ordered_result=TRUE))
  
```



```{r}
fastfood <- fastfood[order(fastfood$calories_type),]
head(fastfood)
```

#6
# Adding facet wrap
```{r}
fastfood %>%
  ggplot(aes(
    x = calories_type,
    fill = calories_type
  ))+
  geom_bar(width=0.75)+
  facet_wrap(~ restaurant)+
  coord_flip()

  
  
```


#7. The second variable should show the percentage of `trans_fat` in `total_fat`. Add the variable to the dataset and call it `trans_fat_percent`. Do not forget to save the updated dataset. 


#trans_fat_percent
```{r}
fastfood<-fastfood%>%
  mutate(total_fat=sum(trans_fat),percent=trans_fat/total_fat,answer_integer=as.integer(restaurant),average=sum(answer_integer=percent))%>%
  ungroup()
```


#8. Create a dataviz that shows the distribution of `trans_fat` in food items for each type of restaurant. Think carefully about the choice of data viz. Use facets, coordinates and theme layers to make your data viz visually appealing and meaningful.

# Starting to visualise

# Adding facet wrap
```{r}
fastfood%>%
  ggplot(aes(
    x = trans_fat,
    fill = restaurant
  ))+
  geom_bar(width=0.75)+
  facet_wrap(~ restaurant)+
  coord_cartesian()+
  theme_minimal()
  
  
```
#9. Calculate the average (mean) total_fat for each type of restaurant. No need to save it as a variable.

```{r}
fastfood%>%
  group_by(restaurant)%>%
  summarise(average_total_fat=mean(total_fat))%>%
  ungroup()
```
#10 create a dataviz that allow to compare different restaurants on this. You can present it on one dataviz (= no facets). Think carefully about the choice of data viz. Use coordinates and theme layers to make your data viz visually appealing and meaningful. 

```{r}
fastfood%>%
  group_by(restaurant)%>%
  summarise(mean_total_fat=mean(total_fat))%>%
  ggplot(aes(restaurant,mean_total_fat, fill=restaurant))+
  geom_col()+
  coord_cartesian(ylim=c(0,40))+
  theme_light()+
  labs(title="compare mean total fat per restaurant")
```

