---
title: "Assignment 1.2"
author: "Lhavanya Thananchayan, s4625955"
date: "5/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Data Wrangling

Install.packages("skimr")
```{r}
library(tidyverse)
library(skimr)
```
Libraries loaded
```{r}
fastfood<-read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
```


`fastfood` variable created

#counting of observations per restaurant
```{r}
fastfood%>%count(restaurant)
```

**Number of observation** for each *restaurant*

#Calculation average calories per restaurant
```{r}
fastfood%>%
  group_by(restaurant)%>%
  summarise(average_calories=mean(calories))%>%
  ungroup()
```
**Average calories** per *restaurant*

#create new variable `average_calories`
```{r}
Average_calories<-fastfood%>%
  group_by(restaurant)%>%
  mutate(average_calories=mean(calories))%>%
  ungroup()

```
New variable `average_calories` created

#Data viz
```{r}
fastfood%>%ggplot(
  aes(total_fat)
)+
  geom_histogram()+
  facet_wrap(vars(restaurant))
```

Total count
```{r}
fastfood%>%
  ggplot(
    aes(total_fat)
  )+
  geom_histogram()
```

Add new variable to data set max_total_fat to calculate the maximum total fat

```{r}
max_total_fat<-fastfood%>%
  group_by(restaurant)%>%
  mutate(max_total_fat=max(total_fat))%>%
  ungroup()
```

max_total_fat variable created, adding to initial data set the max total fat per restaurant
```{r}
fastfood%>%
  group_by(restaurant)%>%
  filter(restaurant=="mcdonalds")%>%
  ggplot(
    aes(x=sugar,
        y=protein,
        colour=restaurant)
  )+
  geom_point()
```

