---
title: "Assignment 01 part 1"
author: "Lhavanya"
date: "6/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



#3. Write 2-3 sentences about RMarkdown (you can google this information or use resources recommended in class - no need to reference)

#4. In the above use bold and italics for editing.


*R Markdown* is a **file** form for making effective documents with R. Its a simple formatting syntax for authorising HTML,PDF and MS word documents to present the data insights and communicate them to stakeholders.


#55. Review the suggested documentation on how to insert links in the .rmd file and include an in-text link to https://rmarkdown.rstudio.com/lesson-8.html


[links](https://rmarkdown.rstudio.com/lesson-8.html)

#6. Insert an R chunk and create a variable with this dataset
https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csvThe name of the variable should be `fastfood`


```{r}
library(tidyverse)
fast_food<-read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
```

#7 Display the first 10 rows of the dataset. Use Help to see how you can do this with `head()` function.

```{r}
fast_food%>%head(10)


```

#8. Display the observations that has more than 1000 calories
```{r}
fast_food%>%filter(calories>1000)
```

#9. Save observations with more than 40 in total_fat and more than 80 in total_carb in a new variable called `dont_eat_this`

```{r}
`dont_eat_this`<-fast_food%>%filter(total_fat>=40 & total_carb>=80)
```

